---
title: "README"
author: "Lutz Gruber"
date: "`r lubridate::today()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is package serves to demonstrate that `testthat::test_local()` (and `devtools::test()`) fail for function `master_fct2()` (when the package is not installed but merely loaded with devtools), but the function runs without any problems when called by the user or when tested with `testthat::test_dir()`.

It is noteworthy that the problem appears to come from a call to `dplyr::summarize()` in the worker function. `master_fct1()` calls a different worker function that does not use `dplyr::summarize()`, and the `testthat::test_local()` has no problems with that function.

## Errors

### Using testthat::test_local()

```{r}
tryCatch(
  expr = { testthat::test_local() },
  error = function(e) {
    print(conditionMessage(e))
  }
)
```

### Using devtools::test()

```{r}
tryCatch(
  expr = { devtools::test() },
  error = function(e) {
    print(conditionMessage(e))
  }
)
```

## No errors

### Using testthat::test_dir()

```{r}
devtools::load_all()

testthat::test_dir("tests/testthat/")
```

### Direct function call

```{r}
devtools::load_all()

master_fct2(5L)
```
